workout_probabilities

### 2019-05-17 workout_probabilities.Rmd

>>>>

# False positive rate control.

We develop a method, following Efron(2008), for controlling the false positive rate.
Every site with sufficient coverage and at least 1 alternate read falls into one of two classes, they are either *null* (non-variant with $\nu = 0$) or *nonnull* (variant with $\nu = \hat{f}$) with prior probabilities $p_0$ and $p_1 = 1-p_0$,

$$
\begin{array}{ll}
p_0 = \textrm{P}\{\textrm{null}\} \quad & \textrm{f}_{0}(\mathbf{x}) \quad \textrm{density if null}\\
p_1 = \textrm{P}\{\textrm{nonnull}\} \quad & \textrm{f}_{1}(\mathbf{x}) \quad \textrm{density if nonnull} .
\end{array}
$$

The local, or site-specific, true positive probability $p_1$ can be estimated as the fraction of all sequenced sites that are expected to be positive.
In a neutrally evolving tumor, the count of variants with a given allele frequency is(bozic et al)
$$
N(f) = \frac{N\mu}{f},
$$
Where $N$ is the total number of sites sequenced and $\mu$ is the per-site mutation probability.
This results in the estimated local nonnull probability
$$
\hat{p}_1 = \frac{N(f)}{N} = \frac{\mu}{f}
$$
and the estimated null probability $\hat{p}_0 = 1 - \hat{p}_1$.
the rest just copies Efron. Time to implement and try to find out how it performs.
